---
title: "R Notebook"
output: html_notebook
---
---
title: "Untitled"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(forecast)
library(tidyverse)
library(fBasics)
library(fGarch)
library(TSA)
library(urca)
```
Load and prep data
```{r}
CC_F <- data.frame(read_csv("~/Downloads/CC=F.csv"))
a.close <- data.frame(date=CC_F$Date, adj.close=as.numeric(CC_F[,6]))
a.close <- a.close[complete.cases(a.close),]

# this is too much data, cut some off to prevent overfitting
a.close <- a.close %>% dplyr::filter(date>'2010-02-26')

# returns, log returns
ac.ret <- returns(a.close$adj.close)[-1]
ac.lr <- log(ac.ret + 1)

ac <- tail(a.close, -1)
ac$logret <- ac.lr
```

```{r}
ac %>% ggplot(aes(x=date, y=adj.close)) + geom_line() + ggtitle('Cocoa Futures') + xlab('Date') + ylab('Adjusted Closing Price')
ac %>% dplyr::filter(date>'2019-02-26')  %>% ggplot(aes(x=date, y=adj.close)) + geom_line() + ggtitle('Cocoa Futures, 2/26/19-2/26/20') + xlab('Date') + ylab('Adjusted Closing Price')

temp <-data.frame(date=tail(ac$date, -1), diffd=diff(ac$adj.close))
temp %>% dplyr::filter(date>'2019-02-26') %>% ggplot(aes(x=date, y=diffd)) + geom_line() + ggtitle('Differenced Cocoa Futures') + xlab('Date') +ylab('Differenced Closing Price')
```
Adjusted closing price
Strong evidence of autocorrelation in the closing price (stat sig box test)- look at differencing to make stationary
```{r}
ac%>% select(adj.close) %>% ggtsdisplay()
Box.test(ac$adj.close, type='Ljung')
ndiffs(ac$adj.close)
```
Try taking log of the data to  make it stationary
```{r}
ac$adj.close %>% log() %>% ggtsdisplay()
Box.test(log(ac$adj.close))
ac$adj.close %>% log() %>% ur.kpss() %>% summary()
# taking the log of the adj closing price does not make it stationary
```

One day difference - does make it stationary
```{r}
ac$adj.close %>% diff() %>% ggtsdisplay()
Box.test(diff(ac$adj.close))
ac$adj.close %>% diff() %>% ur.kpss() %>% summary()
# differenced data is stationary
```
Create a full sequence (including weekends) for differencing
```{r}
fullseq <- data.frame(date = seq(lubridate::ymd('2000-01-01'),lubridate::ymd('2020-02-26'), by='1 day'))
ac.s <- left_join(fullseq, ac)
```
One week difference - still autocorr
```{r}
ac.s$adj.close %>% diff(7) %>% na.omit() %>% ggtsdisplay()
Box.test(na.omit(diff(ac.s$adj.close, lag = 7)))
ac.s$adj.close %>% diff(7) %>% ur.kpss() %>% summary()
#nsdiffs(ac.s$adj.close) Error in nsdiffs(ac.s$adj.close) : Non seasonal data
```

Train/test split, do 1 month of test so 20 days
```{r}
train <- ac %>% dplyr::filter(date<'2020-01-01')
test <- ac %>% dplyr::filter(date>='2020-01-01')
```

Time series regression on the adjusted closing price
```{r}
ac.train.ts <- ts(train$adj.close, frequency=250)
lm1 <- tslm(ac.train.ts ~ trend)
summary(lm1)
lm1.f <- forecast(lm1, h=38, level = 0)
accuracy(lm1.f, test$adj.close)
```

```{r}
lm2 <- tslm(ac.train.ts ~ trend +I(trend^2))
summary(lm2)
lm2.f <- forecast(lm2, h=38, level = 0)
accuracy(lm2.f, test$adj.close)
```

```{r}
lm3 <- tslm(ac.train.ts ~ trend +I(trend^2) + I(trend^3))
summary(lm3)
lm3.f <- forecast(lm3, h=38, level = 0)
accuracy(lm3.f, test$adj.close)
lm3$residuals %>% ggtsdisplay()
# lots of structure in those residuals, maybe plot residuals with an ARIMA?
```

```{r}
lm4 <- tslm(ac.train.ts ~ trend +I(trend^2) + I(trend^3) + I(trend^4))
summary(lm4)
lm4.f <- forecast(lm4, h=38, level = 0)
accuracy(lm4.f, test$adj.close)
## whoah this suddenly got way worse, cubic is best
```

ARIMA of residuals from regression
```{r}
OrderGrid2<-expand.grid(0:2, 0:2, 0:2)

out.mat <- matrix(0, nrow=dim(OrderGrid2)[1], ncol=4)
for (i in 1:dim(OrderGrid2)[1]){
  m=arima(lm3$residuals, 
        order=c(OrderGrid2[i,1],OrderGrid2[i,2],OrderGrid2[i,3]))
  out.mat[i,] <- c(m$aic,
                  sqrt(mean(m$residuals^2)),
                  Box.test(m$residuals,10,type='Ljung')$p.value,
                  Box.test(m$residuals^2,10,type='Ljung')$p.value)
}
out.mat <- data.frame(cbind(OrderGrid2,out.mat))
out.mat[out.mat$X3!=0,]
```
best arima is 2,0,1
```{r}
lm3.res.arima <- Arima(lm3$residuals, order=c(2,0,1))
summary(lm3.res.arima)

lm3.res.arima$residuals %>% ggtsdisplay()
# ersiduals look pretty goos
lm3.res.arima$residuals^2 %>% ggtsdisplay(lag.max=10)
# does look like additional autocorr.
Box.test(lm3.res.arima$residuals, type='Ljung')
# no autocorr. in residuals

#combine the two models
afore <- forecast(lm3.res.arima, 38)
accuracy((lm3.f$mean + afore$mean), test$adj.close)
# test set accuracy is 357.26
sqrt(mean((train$adj.close-(lm3.res.arima$fitted + lm3$fitted.values))^2))
```
ARIMA/aka random walk
```{r}
ac.aa <- auto.arima(train$adj.close)
summary(ac.aa)
ac.aa$residuals %>% ggtsdisplay()
# ersiduals look pretty goos
Box.test(ac.aa$residuals, type='Ljung')
# no autocorr. in residuals

apred <- predict(ac.aa, 38)
accuracy(apred$pred, test$adj.close)
# this just a random walk
```

Decomposition - there is no discernable seasonal component so cannot use decomposition
```{r}
#ac.stl <- stl(train$adj.close, t.window=250, robust=TRUE)
```

Smoothing method
trend, no seasonality
```{r}
s2 <- ets(ac.train.ts, model="ZAN", alpha=0.3)
# relatively slow learner, less dependecy on only the most recent
summary(s2)
s2.f <- forecast(s2, h=38, level = 0)
accuracy(s2.f, test$adj.close)

s2$residuals %>% ggtsdisplay()
Box.test(s2$residuals, type='Ljung')
# additive error, no trend, no seasonality
```
```{r}
plotdf <- test
plotdf$predmean <- lm3.f$mean + afore$mean
plotdf$smooth <- s2.f$mean
plotdf$rw <- apred$pred

plotdf2 <- train
plotdf2$lmar <- lm3$fitted.values + afore$fitted
plotdf2$smooth <- s2.f$fitted
plotdf2$rw <- ac.aa$fitted
#dplyr::filter(plotdf2,date>'2019-02-26')
#cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73","#F0E442", "#0072B2", "#D55E00", "#CC79A7")

ggplot() + geom_line(data=dplyr::filter(train,date>'2018-02-26'), aes(x=date, y=adj.close), color='black') + 
  geom_line(data=plotdf, aes(x=date, y=predmean), color='#E69F00') +   # orange
  geom_line(data=plotdf, aes(x=date, y=smooth), color='#009E73') + #green
 geom_line(data=plotdf, aes(x=date, y=rw), color='#CC79A7')+ #purple
  xlab('Date') + ylab('Adjusted Closing Price') + 
  ggtitle('Forecasted cocoa futures price') + geom_line(data=plotdf, aes(x=date, y=adj.close), linetype=2)
```

